---
title: GLIDER SELECTION DASHBOARD
author: ''
page-layout: full
editor: visual
theme: cosmo
css: kasey_testStyles.css
---


```{r}
#| echo: false
#| message: false
library(bslib)
library(shiny)
```

Comparing the PAM-equipped gliders of the **NOAA Fisheries Glider Rodeo 2026**.

```{ojs}
//| echo: false
data = FileAttachment("gliders_cleaned.csv").csv({typed: true})
duration_min = parseInt(d3.min(data, d => d.endurance_days))
duration_max = parseInt(d3.max(data, d => d.endurance_days))

depth_min = parseInt(d3.min(data, d => d.max_depth_m))
depth_max = parseInt(d3.max(data, d => d.max_depth_m))

speed_min = parseInt(d3.min(data, d => d.speed_kt))
speed_max = parseInt(d3.max(data, d => d.speed_kt))

mass_min = parseInt(d3.min(data, d => d.mass_kg))
mass_max =  parseInt(d3.max(data, d => d.mass_kg))
//No Range, frequency, duty-cycle options here but add them in later
```

## Mission Parameters

1.  Enter requirements for your mission below. Once you click "apply", you will get a list of matching glider options.

<!-- YES/NO Options -->
```{r}
#| echo: false
layout_columns(
  div(
    card( card_header("Capabilities"), 
          card_body( 
            div( style = "display: flex; align-items: center; justify-content: center; gap: 30px; width: 100%;", 
                 div(style = "display: flex; align-items: center;", tags$input(type = "checkbox", id = "rt_checkbox", value = FALSE, style = "margin: 0.2rem 5px 0 0.2rem;"), tags$div(style = "font-size: 0.7rem;", "Real-Time")), 
                 
                 div(style = "display: flex; align-items: center;", tags$input(type = "checkbox", id = "edge_checkbox", value = FALSE, style = "margin: 0.2rem 5px 0 0.2rem;"), tags$div(style = "font-size: 0.7rem;", "Edge-Compute")), 
                 
                 div(style = "display: flex; align-items: center;", tags$input(type = "checkbox", id = "bathy_checkbox", value = FALSE, style = "margin: 0.2rem 5px 0 0.2rem;"), tags$div(style = "font-size: 0.7rem;", "Bathy Drive")), 
                 
                 div(style = "display: flex; align-items: center;", tags$input(type = "checkbox", id = "ice_checkbox", value = FALSE, style = "margin: 0.2rem 5px 0 0.2rem;"), tags$div(style = "font-size: 0.7rem;", "Ice")), 
                 
                 div(style = "display: flex; align-items: center;", tags$input(type = "checkbox", id = "backseat_checkbox", value = FALSE, style = "margin: 0.2rem 5px 0 0.2rem;"), tags$div(style = "font-size: 0.7rem;", "Backseat Drive")) ) ) ),
  
    layout_columns(
      card(
        card_header("Mission Parameters"),
        card_body(
          
          div(
            style = "display: flex; align-items: center; margin-bottom: 2px;",
            tags$input(type = "checkbox", id = "duration_count", style = "margin-right: 5px;"),
            tags$div(style = "font-size: 0.7rem;", "Deployment Duration (Days)")
          ),
          div(
            style = "display: flex; align-items: center; gap: 10px; margin-bottom: 10px; ",
            tags$span(style = "font-size: 0.7rem;", "1"),
            div(
              style = "display: flex; flex-direction: column; align-items: center; flex: 1;",
              tags$input(type = "range", id = "duration_slider", min = "1", max = "660", value = "30", oninput = "document.getElementById('duration_value').textContent = this.value;", style = "width: 100%;"),
              tags$span(id = "duration_value", style = "font-size: 0.7rem;", "30")
            ),
            tags$span(style = "font-size: 0.7rem;", "660")
          ),
          
          div(
            style = "display: flex; align-items: center; margin-bottom: 2px;",
            tags$input(type = "checkbox", id = "depth_count", style = "margin-right: 5px;"),
            tags$div(style = "font-size: 0.7rem;", "Maximum Depth (m)")
          ),
          div(
            style = "display: flex; align-items: center; gap: 10px; margin-bottom: 10px;",
            tags$span(style = "font-size: 0.7rem;", "100"),
            div(
              style = "display: flex; flex-direction: column; align-items: center; flex: 1;",
              tags$input(type = "range", id = "depth_slider", min = "1", max = "1000", value = "30", oninput = "document.getElementById('depth_value').textContent = this.value;", style = "width: 100%;"),
              tags$span(id = "depth_value", style = "font-size: 0.7rem;", "30")
            ),
            tags$span(style = "font-size: 0.7rem;", "1000")
          ),
          
          div(
            style = "display: flex; align-items: center; margin-bottom: 2px;",
            tags$input(type = "checkbox", id = "range_count", style = "margin-right: 5px;"),
            tags$div(style = "font-size: 0.7rem;", "Range (km)")
          ),
          div(
            style = "display: flex; align-items: center; gap: 10px; margin-bottom: 10px;",
            tags$span(style = "font-size: 0.7rem;", "1"),
            div(
              style = "display: flex; flex-direction: column; align-items: center; flex: 1;",
              tags$input(type = "range", id = "range_slider", min = "1", max = "100", value = "30", oninput = "document.getElementById('range_value').textContent = this.value;", style = "width: 100%;"),
              tags$span(id = "range_value", style = "font-size: 0.7rem;", "30")
            ),
            tags$span(style = "font-size: 0.7rem;", "100")
          ),
          
          div(
            style = "display: flex; align-items: center; margin-bottom: 2px;",
            tags$input(type = "checkbox", id = "speed_count", style = "margin-right: 5px;"),
            tags$div(style = "font-size: 0.7rem;", "Speed (kts)")
          ),
          div(
            style = "display: flex; align-items: center; gap: 10px; margin-bottom: 10px;",
            tags$span(style = "font-size: 0.7rem;", "1"),
            div(
              style = "display: flex; flex-direction: column; align-items: center; flex: 1;",
              tags$input(type = "range", id = "speed_slider", min = "1", max = "20", value = "5", oninput = "document.getElementById('speed_value').textContent = this.value;", style = "width: 100%;"),
              tags$span(id = "speed_value", style = "font-size: 0.7rem;", "5")
            ),
            tags$span(style = "font-size: 0.7rem;", "20")
          ),
          
          div(
            style = "display: flex; align-items: center; margin-bottom: 2px;",
            tags$input(type = "checkbox", id = "mass_count", style = "margin-right: 5px;"),
            tags$div(style = "font-size: 0.7rem;", "Maximum Weight (kg)")
          ),
          div(
            style = "display: flex; align-items: center; gap: 10px;",
            tags$span(style = "font-size: 0.7rem;", "1"),
            div(
              style = "display: flex; flex-direction: column; align-items: center; flex: 1;",
              tags$input(type = "range", id = "mass_slider", min = "1", max = "1000", value = "30", oninput = "document.getElementById('mass_value').textContent = this.value;", style = "width: 100%;"),
              tags$span(id = "mass_value", style = "font-size: 0.7rem;", "30")
            ),
            tags$span(style = "font-size: 0.7rem;", "1000")
          )
        )
      ),
      div(
      card(
        card_header("Acoustic Parameters"),
        card_body(
          
          div(
            style = "display: flex; align-items: center; margin-bottom: 2px;",
            tags$input(type = "checkbox", id = "freq_count", style = "margin-right: 5px;"),
            tags$div(style = "font-size: 0.7rem;", "Recording Frequency")
          ),
          div(
            style = "display: flex; align-items: center; gap: 10px; margin-bottom: 10px;",
            tags$span(style = "font-size: 0.7rem;", "1"),
            div(
              style = "display: flex; flex-direction: column; align-items: center; flex: 1;",
              tags$input(type = "range", id = "freq_slider", min = "1", max = "100", value = "30", oninput = "document.getElementById('freq_value').textContent = this.value;", style = "width: 100%;"),
              tags$span(id = "freq_value", style = "font-size: 0.7rem;", "30")
            ),
            tags$span(style = "font-size: 0.7rem;", "100")
          ),
          
          div(
            style = "display: flex; align-items: center; margin-bottom: 2px;",
            tags$input(type = "checkbox", id = "acoustic_depth_count", style = "margin-right: 5px;"),
            tags$div(style = "font-size: 0.7rem;", "Depth")
          ),
          div(
            style = "display: flex; align-items: center; gap: 10px; margin-bottom: 10px;",
            tags$span(style = "font-size: 0.7rem;", "1"),
            div(
              style = "display: flex; flex-direction: column; align-items: center; flex: 1;",
              tags$input(type = "range", id = "acoustic_depth_slider", min = "1", max = "1000", value = "30", oninput = "document.getElementById('acoustic_depth_value').textContent = this.value;", style = "width: 100%;"),
              tags$span(id = "acoustic_depth_value", style = "font-size: 0.7rem;", "30")
            ),
            tags$span(style = "font-size: 0.7rem;", "1000")
          ),
          
          div(
            style = "display: flex; align-items: center; margin-bottom: 2px;",
            tags$input(type = "checkbox", id = "duty_count", style = "margin-right: 5px;"),
            tags$div(style = "font-size: 0.7rem;", "Duty Cycle")
          ),
          div(
            style = "display: flex; align-items: center; gap: 10px;",
            tags$span(style = "font-size: 0.7rem;", "1"),
            div(
              style = "display: flex; flex-direction: column; align-items: center; flex: 1;",
              tags$input(type = "range", id = "duty_slider", min = "1", max = "100", value = "30", oninput = "document.getElementById('duty_value').textContent = this.value;", style = "width: 100%;"),
              tags$span(id = "duty_value", style = "font-size: 0.7rem;", "30")
            ),
            tags$span(style = "font-size: 0.7rem;", "100")
          )
        )
      ), 
      tags$button(id = "apply_button",class = "btn btn-primary",style =  "display: block; width: 100%; padding: 4px 10px; margin: 10px 0 0 0;","Apply")),
      
      col_widths = c(6, 6)
    )
  ),
  
  col_widths = c(12)
)
```

```{ojs}
//| echo: false
//| output: false

[
  ["duration_slider", duration_min, duration_max],
  ["depth_slider", depth_min, depth_max],
  ["speed_slider", speed_min, speed_max],
  ["mass_slider", mass_min, mass_max]
].forEach(([id, min, max]) => {
  const slider = document.getElementById(id)
  slider.min = min
  slider.max = max
  slider.parentElement.parentElement.firstElementChild.textContent = min
  slider.parentElement.parentElement.lastElementChild.textContent = max
})
```

## Your Options
<!-- Expose my shiny R objects to OJS to work with Anne's chart -->
```{ojs}
//| echo: false
apply = Generators.input(document.getElementById("apply_button"))
```

```{ojs}
//| echo: false
filtered = { apply;
if (!data || !Array.isArray(data)) return [];
return data.filter(g => {
  if (document.getElementById("duration_count").checked && g.endurance_days != null && g.endurance_days < Number(document.getElementById("duration_slider").value)) return false
  if (document.getElementById("depth_count").checked && g.max_depth_m != null && g.max_depth_m < Number(document.getElementById("depth_slider").value)) return false
  if (document.getElementById("speed_count").checked && g.speed_kt != null && g.speed_kt < Number(document.getElementById("speed_slider").value)) return false
  if (document.getElementById("mass_count").checked && g.mass_kg != null && g.mass_kg > Number(document.getElementById("mass_slider").value)) return false
  if (document.getElementById("ice_checkbox").checked && g.ice_capable !== true && g.ice_capable !== "yes") return false
  if (document.getElementById("rt_checkbox").checked && g.real_time_comms !== "yes") return false

  return true;
});
}
  // Add these back when the spreadsheet has the corresponding columns:
  // if (document.getElementById("range_count").checked && g.range_km != null && g.range_km < Number(document.getElementById("range_slider").value)) return false
  // if (document.getElementById("edge_checkbox").checked && g.edge_compute !== true && g.edge_compute !== "Yes") return false
  // if (document.getElementById("bathy_checkbox").checked && g.bathy_drive !== true && g.bathy_drive !== "Yes") return false
  // if (document.getElementById("backseat_checkbox").checked && g.backseat_drive !== true && g.backseat_drive !== "Yes") return false
```

```{ojs}
//| echo: false
Inputs.table(filtered, {
  columns: [
    "manufacturer", "glider", "max_depth_m", "endurance_days",
    "speed_kt", "mass_kg", "real_time_comms", "acoustic_sensor", "ice_capable"
  ],
  header: {
    manufacturer: "Manufacturer",
    glider: "Glider",
    max_depth_m: "Max depth (m)",
    endurance_days: "Endurance (days, est.)",
    speed_kt: "Speed (kt, est.)",
    mass_kg: "Mass (kg)",
    real_time_comms: "Real-time comms",
    acoustic_sensor: "Acoustic sensor",
    ice_capable: "Ice capable"
  }
})
```


## Glider Comparisons
Please see below for details of your chosen gliders. 
```{r}
#| echo: false

layout_columns(
card( card_body(
  tags$div(style =  "height: 150px; margin-bottom: 0;", class = "comparison-image"),
  tags$div(class = "comparison-label", ""), 
  tags$div(class = "comparison-row", "Deployment Duration"),
  tags$div(class = "comparison-row", "Depth Range"),
  tags$div(class = "comparison-row", "Base Weight"),
  tags$div(class = "comparison-row", "Range"),
  tags$div(class = "comparison-row", "Speed"),
)),
card(card_header("Glider 1"),
     card_body(img(src = "/content/images/glider_holdImage.jpg", style = "height: 100px;  margin-bottom: 0;", class = "comparison-image"),
               tags$div(class = "comparison-row", "1–20 days"),
               tags$div(class = "comparison-row", "0-1000m"),
               tags$div(class = "comparison-row", "85kg"),
               tags$div(class = "comparison-row", "2 km"),
               tags$div(class = "comparison-row", "1 kt"),
               )),
card(card_header("Glider 2"),
     card_body(img(src = "/content/images/glider_holdImage.jpg", style = "height: 100px;  margin-bottom: 0;", class = "comparison-image"),
               tags$div(class = "comparison-row", "1–20 days"),
               tags$div(class = "comparison-row", "0-1000m"),
               tags$div(class = "comparison-row", "85kg"),
               tags$div(class = "comparison-row", "2 km"),
               tags$div(class = "comparison-row", "1 kt"),
               )),
card(card_header("Glider 3"),
     card_body(img(src = "/content/images/glider_holdImage.jpg", style = "height: 100px;  margin-bottom: 0;", class = "comparison-image"),
               tags$div(class = "comparison-row", "1–20 days"),
               tags$div(class = "comparison-row", "0-1000m"),
               tags$div(class = "comparison-row", "85kg"),
               tags$div(class = "comparison-row", "2 km"),
               tags$div(class = "comparison-row", "1 kt"),
               )),
card(card_header("Glider 4"),
     card_body(img(src = "/content/images/glider_holdImage.jpg", style = "height: 100px;  margin-bottom: 0;", class = "comparison-image"),
               tags$div(class = "comparison-row", "1–20 days"),
               tags$div(class = "comparison-row", "0-1000m"),
               tags$div(class = "comparison-row", "85kg"),
               tags$div(class = "comparison-row", "2 km"),
               tags$div(class = "comparison-row", "1 kt"),
               ))
)
```

Each panel below is a different metric, shown as a percentage of the highest value among the currently matching gliders (so depth in meters, endurance in days, and speed in knots can sit side by side on one chart). Hover a bar to see the raw value.

```{ojs}
//| echo: false

// ---- RESHAPE FOR FACETED COMPARISON ----
// Add/remove entries here to change which metrics appear in the comparison chart.

metricList = [
  {key: "max_depth_m", label: "Max depth (m)"},
  {key: "endurance_days", label: "Endurance (days)"},
  {key: "speed_kt", label: "Speed (kt)"}
]

longData = filtered.flatMap(g =>
  metricList
    .map(m => ({glider: g.glider, metric: m.label, value: g[m.key]}))
    .filter(d => d.value != null)
)

maxByMetric = d3.rollup(longData, v => d3.max(v, d => d.value), d => d.metric)

normalizedData = longData.map(d => ({
  ...d,
  pct: maxByMetric.get(d.metric) > 0 ? (d.value / maxByMetric.get(d.metric)) * 100 : 0
}))
```

```{ojs}
//| echo: false
Plot.plot({
  marginLeft: 100,
  fx: {label: null},
  x: {label: "% of max among matching gliders", domain: [0, 100]},
  y: {label: null},
  color: {legend: false},
  marks: [
    Plot.barX(normalizedData, {
      x: "pct",
      y: "glider",
      fx: "metric",
      fill: "metric",
      sort: {y: "-x"},
      title: d => `${d.glider}: ${d.value}`
    }),
    Plot.ruleX([0])
  ]
})
```

